### 2019-10-04 paper/paper.tex
Minor

Complex structure can indeed be observed in protein expression for some genes,
such as the molecules Bhlhb5 \citep{Joshi2008} and Lmo4
\citep{Cederquist2013,Greig2013}. These expression patterns can therefore
provide a theoretical mechanism for the guidance of axons into distinct
regions, shifting the explanation of how such structures are generated into
the realm of gene transcriptional interactions and mRNA diffusion/movement
(\cmnt{Fixme: find a ref on structure in gene transcription}). However,
complex, stable structure in gene expression is less commonly reported than
homogeneous or simply varying expression, such as Pax6, Emx2, Coup-TF1 which
display graded expression across the entire isocortex
(\cmnt{REFS}). Furthermore, the complex structure observed in the whisker
barrel field has not, to our knowledge, been linked to a complex set of gene
expression patterns matching the scale of the barrels. To investigate how the
whisker barrel structure might form in the presence of only two
coordinate-giving morphogen gradients, we turned our attention to the
competition for connections built into the model.

>>>>

Complex structure can indeed be observed in protein expression for some genes,
such as the molecules Bhlhb5 \citep{Joshi2008} and Lmo4
\citep{Cederquist2013,Greig2013}. These expression patterns can therefore
provide a theoretical mechanism for the guidance of axons into distinct
regions, shifting the explanation of how such structures are generated into
the realm of gene transcriptional interactions and mRNA diffusion/movement
(\cmnt{Fixme: find a ref on structure in gene transcription}). However,
complex, stable structure in gene expression is less commonly reported than
homogeneous or simply varying expression, such as Pax6, Emx2, Sp8 and Coup-tf1 which
display graded expression across the entire isocortex
(\cmnt{REFS}). Furthermore, the complex structure observed in the whisker
barrel field has not, to our knowledge, been linked to a complex set of gene
expression patterns matching the scale of the barrels. To investigate how the
whisker barrel structure might form in the presence of only two
coordinate-giving morphogen gradients, we turned our attention to the
competition for connections built into the model.
